\graphicspath{{conclusion/fig/}}

\chapter{Summary and Conclusion}
\label{chap:conclusion}
\vspace{-3em}
\section{Summary}

%List objectives and methods and what was gotten
The objective of this thesis was to design and build a solution to measure the air quality inside taxis and at taxi ranks. The solution built has sensors that measure CO2, particulate matter, VOC, NOx, relative humidity and temperature. The solution stores this data locally and is able to communicate between devices making it portable and easily transportable, as was the goal. The solution features connectivity and data acquisition methods, extended battery life and communication capabilities.


\section{Conclusion}
%then conclusion, so what... what do you tell your granny
\noindent
The primary objectives were achieved in this report and the communication of the module worked better than expected. The solution developed is considered to be viable for deployment and data gathering. The solution can be implemented anywhere where there is access to at least 5V 2A power.
%future work or recommendations
\section{Future work and recommendations}
Some possible design improvements include hot swappable battery with internal battery to keep the sensors online and not have them lose calibration. In future iterations it would be beneficial to follow a more vertical approach to mounting the sensors, in this iteration it was rather difficult given the difficulty in working with the SEN55 sensor's connector. The vertical approach would lessen the footprint of the module making it easier to mount. I would consider LiFePO4 batteries, specifically the 32700 cell batteries to be the ideal replacement for the LiPo batteries currently in the module, they have far superior cycle performance and are much less prone to swelling. All of the sensors used in this project, besides the obvious GPS sensor, can be calibrated. They include methods for this in their various documentation, if the product were to be mass produced it would be beneficial to have an auto calibrate function to a known value. Another more interesting addition would be an RGB indicator LED to give data to the outside, with the current setup there is no indication that the device is functional other than current draw and the base station connecting to the network.